---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Assignment 2 - rbpack

<!-- badges: start -->
<!-- badges: end -->

The goal of Assignment 2 - rbpack is to create a package of functions.

The rbpack was created by Raveen Badyal for STAT545B Assignment 2. It is a package that includes an lb_to_kg function. To use this function, you will have to install the package. The package can be installed using install_github("stat545ubc-2023/rbpack"). The package can then be loaded using the library() function.
```{r}
library(rbpack)
```

The lb_to_kg function can be used to convert pounds to kilograms to 2 decimal
places. A numeric input is required for the lb_to_kg function. Numbers less than 0.02 can not be inputted into this function as the outut is limited to two decimal places. A different function must be used for that purpose, or divide by 2.20462. There are some examples below. Error messages will be outputted if an invalid input is made.

```{r}
lb_to_kg(0.02)
lb_to_kg(0.01)
lb_to_kg(10)
lb_to_kg("hi")
```
```
